Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-28 article.tex
Updates to Sec 4.2

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall, rounded to the nearest second) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using a Mac Studio with an M2 Ultra CPU on one CPU core, where the code was built with the Clang compiler.
\hl{Present data for one hardware first, and give comparison after.}
Examination of multi-CPU-core parallelisation is left to Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{ll|ll|ll}
			\hline
			Case & Cell Count & \multicolumn{2}{c|}{JFNK} & \multicolumn{2}{c}{Segregated} \\
			     &            & Time (s) & Memory (MB) & Time (s) & Memory (MB) \\
			\hline 
			MMS & 384 & 0 & $78$ & X & Y \\
				& $4\,374$ & 0 & $86$ & X & Y \\
				& $41\,154$ & 1 & $195$ & X & Y \\
				&  $355\,914$ & 4 & $1\,063$ & X & Y \\
				& $2\,958\,234$ & 41 & $6\,724$ & X & Y \\
				& $24\,118\,074$ & 486 & $30\,606$ & X & Y \\
			\hline
			Elliptic & 45 & 0 & $72$ & X & Y \\
				& 472 & 0 & $78$ & X & Y \\
				& $4\,140$ & 1 & $153$ & X & Y \\
				& $34\,968$ & 7 & $754$ & X & Y \\
				& $287\,280$ & 95 & $3\,943$ & X & Y \\
				& $2\,438\,242$ & 988 & $21\,884$ & X & Y \\
			\hline
			T-member & 624& 0 & 84 & X & Y \\
				& $4\,992$ & 1 & 127 & X & Y \\
				& $39\,936$ & 10 & 557 & X & Y \\
				& $319\,488$ & 154 & $4\,024$ & X & Y \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ & X & Y \\
			\hline
			Ventricle & $1\,620$ & 54 & 133 & & \\
				& $12\,960$ & 576 & 553 & & \\
				& $103\,680$ & $8\,362$ & $3\,435$ & & \\
				& $829\,440$ & $150\,023$ & $11\,746$ & & \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }
	\label{tab:times_memory}
\end{table}

>>>>

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall, rounded to the nearest second) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using a Mac Studio with an M2 Ultra CPU on one CPU core, where the code was built with the Clang compiler.
\hl{Present data for one hardware first, and give comparison after.}
Examination of multi-CPU-core parallelisation is left to Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{ll|ll|ll}
			\hline
			Case & Cell Count & \multicolumn{2}{c|}{JFNK} & \multicolumn{2}{c}{Segregated} \\
			     &            & Time & Memory & Time & Memory \\
			     &            & (in s) & (in MB) & (in s) & (in MB) \\
			\hline 
			MMS & 384 & 0 & $78$ & X & Y \\
				& $4\,374$ & 0 & $86$ & X & Y \\
				& $41\,154$ & 1 & $195$ & X & Y \\
				&  $355\,914$ & 4 & $1\,063$ & X & Y \\
				& $2\,958\,234$ & 41 & $6\,724$ & X & Y \\
				& $24\,118\,074$ & 486 & $30\,606$ & X & Y \\
			\hline
			Elliptic & 45 & 0 & $72$ & X & Y \\
				& 472 & 0 & $78$ & X & Y \\
				& $4\,140$ & 1 & $153$ & X & Y \\
				& $34\,968$ & 7 & $754$ & X & Y \\
				& $287\,280$ & 95 & $3\,943$ & X & Y \\
				& $2\,438\,242$ & 988 & $21\,884$ & X & Y \\
			\hline
			T-member & 624& 0 & 84 & X & Y \\
				& $4\,992$ & 1 & 127 & X & Y \\
				& $39\,936$ & 10 & 557 & X & Y \\
				& $319\,488$ & 154 & $4\,024$ & X & Y \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ & X & Y \\
			\hline
			Ventricle & $1\,620$ & 54 & 133 & & \\
				& $12\,960$ & 576 & 553 & & \\
				& $103\,680$ & $8\,362$ & $3\,435$ & & \\
				& $829\,440$ & $150\,023$ & $11\,746$ & & \\
			\hline
			Membrane i & $x$ & x & x & & \\
			\hline
			Membrane ii & $x$ & x & x & & \\
			\hline
			Membrane iii & $x$ & x & x & & \\
			\hline
			Cantilever & $x$ & x & x & & \\
			\hline
			Turbine & $x$ & x & x & & \\
			\hline
			FSI & $x$ & x & x & & \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }
	\label{tab:times_memory}
\end{table}
